% !TEX root = ../../recipes.tex

\begin{recipe}{Southwest Casserole}{serves 6}{375\0}
    \ingredient[1]{lb}{Ground beef}
    Brown and drain ground beef.

    \ingredient[1]{11oz can}{Cream of chicken soup}
    \ingredient[$\frac{1}{2}$]{cup}{Milk}
    \ingredient[1]{4oz can}{Green chiles}
    Add soup, milk, and chiles. Simmer for 3 minutes.

    \ingredient[12]{}{Small flour tortillas, cut into 2 inch strips}
    \ingredient[1]{20oz can}{Mild enchilada sauce}
    \ingredient[1]{cup}{Shredded cheddar cheese}
    Arrange half of the tortilla strips in the bottom of a greased $9 \times 13$ inch pan. Cover with half of the enchilada sauce and half of the beef mixture. Repeat layer and cover with cheese.

    \newstep
    Bake at 375\0 for 25 minutes.

\end{recipe}

\begin{recipe}{Effie Chicken}{serves 4}{350\0}
    \ingredient[3]{cups}{Chopped, cooked chicken}
    \ingredient[1]{11oz can}{Cream of chicken soup}
    \ingredient[1]{16oz pkg}{Sour cream}
    \ingredient[3]{tsp}{Poppy seeds}
    Combine chicken, soup, sour cream, and poppy seeds. Spread mixture into lightly greased $11\times7$ pan.

    \ingredient[1]{tube}{Crushed Ritz crackers}
    \ingredient[$\frac{1}{4}$]{cup}{Melted butter}
    Mix crumbs and butter. Spread over chicken mixture.

    \newstep
    Bake at 350\0 for 35 to 40 minutes, or until bubbly.
\end{recipe}

\begin{recipe}{Polish Sausage Thing}{Serves 4}{425\0}
    \ingredient[1]{lb}{Fully cooked, chopped, Polish sausage}
    \ingredient[1]{can}{drained sauerkraut}
    \ingredient[1]{cup}{apple cider or juice}
    Layer sausage and sauerkraut in large pan. Pour apple cider into pan.

    \newstep
    Cover with foil and bake for 30--40 minutes. Remove from oven.

    \ingredient[$1\frac{1}{2}$]{cup}{Bisquick mix}
    \ingredient[$\frac{1}{2}$]{cup}{milk}
    \ingredient[$\frac{1}{2}$]{cup}{shredded cheddar}
    \ingredient[1]{}{egg}
    \ingredient[1]{tbsp}{fresh chopped parsely}
    Mix remaining ingredients until soft dough forms. Drop in large spoonfuls onto sausage mixture.

    \newstep
    Bake uncovered for 10--12 minutes, or until biscuits are cooked and golden brown.
\end{recipe}
