% !TEX root = ../../recipes.tex

\begin{recipe}{Lasagna}{serves 6}{375\0}
    \ingredient[1.5]{lb}{Ground beef}
    \ingredient[1.5]{lb}{Ground italian sausage}
    Brown and drain ground beef and sausage.

    \ingredient[1]{15oz can}{Tomato sauce}
    \ingredient[$\frac{1}{2}$]{cup}{Water}
    \ingredient[2]{tsp}{Brown sugar}
    \ingredient[$1\frac{1}{2}$]{tsp}{Salt}
    \ingredient[1]{tsp}{Oregano}
    \ingredient[$\frac{1}{2}$]{tsp}{Garlic powder}
    \ingredient[$\frac{1}{4}$]{tsp}{Pepper}
    Add tomato sauce, water, and seasonings to meat. Heat to boiling and simmer for 30 minutes, stirring often.

    \ingredient[1]{8oz pkg}{Lasagna noodles}
    Cook noodles as directed on package. Drain.

    \ingredient[1]{}{Egg}
    \ingredient[2]{16oz pkg}{Cottage cheese}
    Beat egg and combine with cottage cheese.

    \ingredient[2]{8oz pkg}{Shredded mozzarella cheese}
    Place half of noodles in a $9 \times 13$ inch pan (or larger). Cover with half of the meat sauce. Spoon half the cottage cheese mixture over noodles and cover with half of the mozzarella cheese. Repeat layer in same order.

    \newstep
    Bake at 375\0 for 45 minutes. Let sit for 10 minutes before serving.
\end{recipe}

\begin{recipe}{Carbonara}{Serves 3}{}
    \ingredient[2]{}{whole eggs}
    \ingredient[2]{}{egg yolks}
    \ingredient{small bit}{drained pasta water}
    \ingredient{}{black pepper}
    \ingredient{some}{fried pancetta cubes}
    Whisk sauce together.

    \ingredient[]{enough}{pasta}
    Mix sauce with pasta and stir until sauce thickens.

    \ingredient{}{parmesan}
    Top with parmesan.
\end{recipe}

\begin{recipe}{Italian Bean and Sausage Pasta}{Serves 4}{}
    \ingredient[1]{tbsp}{olive oil}
    \ingredient[16]{oz}{Italian sausage links}
    Heat oil over medium heat. Brown sausages.

    \ingredient[8]{oz}{uncooked pasta}
    \ingredient[2]{cups}{chicken broth}
    \ingredient[2]{tbsp}{tomato paste}
    \ingredient[$\frac{1}{2}$]{tsp}{salt}
    Add pasta, broth, sauce, and salt. Heat to boiling, cover, and reduce heat. Cook for 9 to 11 minutes, stirring occasionally.

    \ingredient[1]{large can}{cannellini beans}
    \ingredient[$\frac{1}{2}$]{cup}{grated parmesan cheese}
    Add beans and cook for 3 to 4 minutes. Stir in parmesan cheese and serve.
\end{recipe}

\begin{recipe}{Sausage and Penne Casserole}{Serves 4}{350\0}
    \ingredient[8]{oz}{penne or macaroni pasta}
    Cook, drain, and rinse pasta.

    \ingredient[16]{oz}{andouille sausage, thinly sliced}
    Cook sausage, and set aside.

    \ingredient[2]{tbsp}{butter}
    \ingredient[2]{tbsp}{flour}
    \ingredient[$1\frac{1}{2}$]{cup}{milk}
    \ingredient[1]{tsp}{Creole seasoning}
    \ingredient[2]{cups}{shredded cheddar}
    In same skillet over medium heat, melt butter and mix with flour. Gradually add milk and Creole seasoning. Cook until thickened, stirring constantly. Add cheese and stir until melted.

    \ingredient[1]{cup}{fine bread crumbs, tossed with 2 tsp melted butter}
    Add the pasta and sausage. Mix and add to greased pan.

    \newstep
    Bake for 30 minutes.
\end{recipe}

\begin{recipe}{Andouille Mac \& Cheese}{Serves 4}{350\0}
    \ingredient[8]{oz}{macaroni pasta}
    Cook and drain pasta.

    \ingredient[1--2]{tsp}{olive oil}
    \ingredient[16]{oz}{andouille sausage, thinly sliced}
    \ingredient[6]{}{green onions, thinly sliced}
    \ingredient[1]{clove}{minced garlic}
    Brown sausage and add onion and garlic. Set aside.

    \ingredient[4]{tbsp}{butter}
    \ingredient[$\frac{1}{4}$]{cup}{flour}
    \ingredient[1]{tsp}{cajun seasoning}
    \ingredient[]{}{black pepper}
    \ingredient[$2\frac{1}{3}$]{cup}{milk}
    Melt butter in same skillet, add flour and stir until smooth. Cook for 2 minutes, continually stirring. Add seasoning. Gradually add milk. Cook until thickened, continually stirring.

    \ingredient[3]{cup}{shredded cheddar, divided}
    Add 2 cups of the cheese, stirring until melted. Spoon into greased pan.

    \newstep
    Top with remaining cheese and back for 20--25 minutes.
\end{recipe}
