% !TEX root = ../../recipes.tex

\begin{recipe}{Cheeseburger Pie}{serves 4}{350\0}
    \ingredient[2]{pkg}{Crescent rolls}
    Lay one package of crescent rolls in a $9 \times 13$ pan.

    \ingredient[2]{lb}{Ground beef}
    \ingredient[1]{8oz can}{Tomato sauce}
    \ingredient[1]{pkg}{Sloppy joes mix}
    \ingredient{}{Oregano}
    Brown and drain ground beef. Add tomato sauce, sloppy joes mix, and oregano to taste. Spread over dough.

    \ingredient[1]{pkg}{Shredded mozzarella cheese}
    \ingredient[1]{pkg}{Shredded cheddar cheese}
    Cover beef mixture with cheese, and top with second package of crescent rolls.

    \newstep
    Bake at 350\0 for 25 minutes
\end{recipe}

\begin{recipe}{Bean Pie}{serves 6}{425\0}
    \ingredient[1]{lb}{Ground beef}
    \ingredient[2--3]{cloves}{Minced garlic}
    Brown and drain beef and garlic.

    \ingredient[1]{12oz can}{Condensed bean and bacon soup}
    \ingredient[1]{cup}{Picante sauce}
    \ingredient[$\frac{1}{4}$]{cup}{Cornstarch}
    \ingredient[1]{Tbsp}{Chopped parsley}
    \ingredient[1]{tsp}{Salt}
    \ingredient[$\frac{1}{4}$]{Black pepper}
    In large bowl, mix soup, picante sauce, corstarch, and seasonings.

    \ingredient[1]{16oz can}{Kidney beans, rinsed and drained}
    \ingredient[1]{15oz can}{Black beans, rinsed and drained}
    \ingredient[2]{cups}{Shredded cheddar cheese, divided}
    \ingredient[$\frac{3}{4}$]{cup}{Sliced green onions, divided}
    Add beans, $1\frac{1}{4}$ cup cheese, $\frac{1}{2}$ cup green onions, and beef to bean mixture.

    \ingredient{}{Pastry for 10-inch double crust pie}
    Line deep pie pan with bottom pastry, and fill with bean mixture. Top with remaining pastry. Seal and flute edges, and cut slits in top crust.

    \newstep
    Bake at 425\0 for 30--35 minutes, or until slightly browned. Cool for 5 minutes before cutting.

    \newstep
    Garnish with sour cream, remaining cheese, and remaining green onions.
\end{recipe}
